---
title: "Session 4 | gather/spread"
author: "보아즈 시각화"
date: "2019년 1월 28일"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)

```

#### Converting Data

```{r}
olddata_wide <- read.table(header=TRUE, text='
 subject sex control cond1 cond2
                           1   M     7.9  12.3  10.7
                           2   F     6.3  10.6  11.1
                           3   F     9.5  13.1  13.8
                           4   M    11.5  13.4  12.9
                           ')
# Make sure the subject column is a factor
olddata_wide$subject <- factor(olddata_wide$subject)

olddata_long <- read.table(header=TRUE, text='
 subject sex condition measurement
                           1   M   control         7.9
                           1   M     cond1        12.3
                           1   M     cond2        10.7
                           2   F   control         6.3
                           2   F     cond1        10.6
                           2   F     cond2        11.1
                           3   F   control         9.5
                           3   F     cond1        13.1
                           3   F     cond2        13.8
                           4   M   control        11.5
                           4   M     cond1        13.4
                           4   M     cond2        12.9
                           ')
# Make sure the subject column is a factor
olddata_long$subject <- factor(olddata_long$subject)

```



#### tidyr
#### 1. From wide to long

```{r}
olddata_wide

```

##### The arguments to gather():
- data: Data object
- key: Name of new key column (made from names of data columns)
- value: Name of new value column
- ...: Names of source columns that contain values
- factor_key: Treat the new key column as a factor (instead of character vector)

```{r}
data_long <- gather(olddata_wide, condition, measurement, control:cond2, factor_key=TRUE)
data_long
```


####2. From long to wide 

```{r}
olddata_long
```



##### The arguments to spread():
- data: Data object
- key: Name of column containing the new column names
- value: Name of column containing values

```{r}
data_wide <- spread(olddata_long, condition, measurement)
data_wide
```

